Joint Neighborhood Subgraphs Link Prediction

### 2017-06-29 paper.tex
Add files via upload

\section{Method}
In this section, we describe our proposed link prediction method which is based on the graph structure exploitation only.
\subsection{Definitions and notation}
We consider a graph $G=(V,E)$ where $V$ is the set of nodes and $E$ is the set of links. The set $E$ can be devided into a subset of observed links ($O$) and a subset of unobserved links ($U$). The problem is that the set $O$ is not a complete set. Therefore, \textit{link prediction} is the task that aims at exploiting graph structure to rank links in $U$ from the most to the least probable to be considered as observed links in $O$.

The \textit{distance} between two nodes $u$ and $v$, notated as $\mathcal{D}(u,v)$, is the length of the shortest path between them. The \textit{neighborhood} with radius $r$ of a node $v$ is the set of nodes
at a distance no greater than $r$ from $v$ and denoted by $N_r(v)$. The \textit{neighborhood subgraph} with radius $r$ of node $v$, denoted by $\mathcal{N}_{r}^{v}$,  is the subgraph formed by the nodes in the
neighborhood with radius $r$ of $v$ and the relative edges with endpoints in $N_r(v)$. The degree of a node $u$ denoted as $d(u)$ is the number of its neighborhood $d(u) = \mathcal{N}_{1}^{u}$.
\subsection{The neighborhood subgraph pairwise distance kernel}
The NSPDK \cite{nspdk} is an instance of convolution kernel \cite{convolution-kernel} where given a graph $G \in \mathcal{G}$ and two rooted graphs $A_u, B_v$, the relation $R_{r,d}(A_u, B_v, G)$ is true {\em iff} $A_u \cong \mathcal{N}_r^u$ is (up to isomorphism $\cong$) a neighborhood subgraph of radius $r$ of $G$ and so is $B_v \cong  \mathcal{N}_r^v$, with roots at distance $\mathcal{D}(u,v)= d$. We denote $R^{-1}$ as the inverse relation that returns all pairs of neighborhoods of radius $r$ at distance $d$ in $G$, $R^{-1}_{r,d}(G) = \lbrace A_u, B_v | R_{r,d}(A_u,B_v,G)=true\rbrace$. The kernel $\kappa_{r,d}$ over $\mathcal{G} \times \mathcal{G}$, counts the number of such fragments in common in two input graphs: 
\begin{center}
$\kappa_{r,d}(G,G^{'}) = 
\!\!\!\!\!\!\!\!\!\!\!\! 
\sum\limits_{\substack{A_u, B_v \ \in \ R_{r,d}^{-1}(G) \\ 
{A'}_{u'}, {B'}_{v'} \ \in \ R_{r,d}^{-1}(G')
}} \!\!\!\!\!\!\!\!\!\!\!\!  { { \textbf{1}_{A_{u} \cong A'_{u'}}} \cdot {
\textbf{1}_{B_{v} \cong B'_{v'}}} }$, 
\end{center}
\noindent where $\textbf{1}_{A \cong B}$ is the \textit{exact matching function} that returns 1 if $A$ is
isomorphic to $B$ and 0 otherwise.  Finally, the NSPDK is defined as $K(G,G') = \sum\limits_{r}{\sum\limits_{d}{\kappa_{r,d}(G,G')}}$, where for efficiency reasons, the values of $r$ and $d$ are upper bounded to a given maximal $r^*$ and $d^*$, respectively.

@@

\item \textit{Metabolic} \cite{metabolic}: a biological network which relates enzyme proteins and chemical compounds and includes 668 nodes and 2782 links.

\item \textit{Nips} \cite{nips}: a network of co-authors at NIPS conference containing 2865 nodes and 4733 links.

@@

\item \textit{Conflict} \cite{conflict1}, \cite{conflict2}: a network describing the dispute between countries. It consists of 130 nodes and 180 links.

@@

\hline
         & \multicolumn{6}{c|}{\textbf{Datasets}}\\
 \hline
\textbf{Methods} & Protein & Metabolic & Nips & Condmat & Conflict & PowerGrid\\
\hline
AA & 56.4$\pm$0.5 & 52.4$\pm$0.5 & 51.2$\pm$0.2 & 56.7$\pm$1.4 & 50.7$\pm$0.8 & 58.9$\pm$0.3\\
PA & 75.0$\pm$0.3 & 52.4$\pm$0.5 & 54.3$\pm$0.5 & 71.6$\pm$2.6 & 54.6$\pm$2.4 & 44.2$\pm$01.0\\
SHP & 72.6$\pm$0.5 & 62.6$\pm$0.4 & 51.7$\pm$0.3 & 67.3$\pm$1.8 & 51.2$\pm$1.4 & 65.9$\pm$1.5\\
Katz & 72.7$\pm$0.5 & 60.8$\pm$0.7 & 51.7$\pm$0.3 & 67.3$\pm$1.7 & 51.2$\pm$1.4 & 65.5$\pm$1.6 \\
Sup-Top & 75.4$\pm$0.3 & 62.8$\pm$0.1 & 54.2$\pm$0.7 & 72.0$\pm$2.0 & 69.5$\pm$7.6 & 70.8$\pm$6.2\\
SVD & 63.5$\pm$0.3 & 53.8$\pm$1.7 & 51.2$\pm$3.1 & 62.9$\pm$5.1 & 54.1$\pm$9.4 & 69.1$\pm$2.6\\
Fact+Scores & 79.3$\pm$0.5 & 69.6$\pm$0.2 & 61.3$\pm$1.9 & 81.2$\pm$2.0 & 68.9$\pm$4.2 & 75.1$\pm$2.0 \\
JNSL & 80.1$\pm$0.8 & 72.5$\pm$0.7 & 62.1$\pm$0.8 & 88.6$\pm$2.3 & 72.0$\pm$0.9 & 75.6$\pm$0.7 \\
 \hline 
\end{tabular}
\label{result_table}
\end{table}
\section{Conclusion and Future Work}
In this paper, we have proposed an effective method for link prediction. Our method takes advantages from the way to represent links as joint neighborhood subgraphs and the employment of an convolution kernel that is able to efficiently exploit the graph structure. The results from the experiment show that our method is the state of the art for graph structured link prediction, especially when the side information are not available.

>>>>

\section{Method}
In this section, we describe our proposed link prediction method which is based on the graph structure exploitation only.
\subsection{Definitions and notation}
We consider a graph $G=(V,E)$ where $V$ is the set of nodes and $E$ is the set of links. The set $E$ can be devided into a subset of observed links ($O$) and a subset of unobserved links ($U$). It is often that the set $O$ is not a complete set since they are many actual links are missing. Therefore, finding most likely set of links in $U$ to be considered as the complement set of $O$ is an important task which impacts on the performance of graph-based systems. Link prediction is the task that aims at exploiting graph structure to rank links in $U$ from the most to the least probable to be considered as observed links in $O$.

We define the \textit{distance} between two nodes $u$ and $v$, notated as $\mathcal{D}(u,v)$, is the length of the shortest path between them. The \textit{neighborhood} of a node $u$ with radius $r$ is the set of nodes such that they are at distance no greater than $r$ from $u$ and it is denoted by $N_r(u)$ and $N_r(u) = \lbrace v\ |\ d(u,v) \leq r \rbrace$. The \textit{neighborhood subgraph} with radius $r$ of a given node $u$, denoted by $\mathcal{N}_{r}^{u}$, is the subgraph formed by the nodes in the
\textit{neighborhood} with radius $r$ of $u$ and the relative edges with endpoints in $N_r(u)$. The degree of a node $u$ denoted as $d(u)$ is the cardinality of its neighborhood $d(u) = |\mathcal{N}_{1}^{u}|$.
\subsection{The neighborhood subgraph pairwise distance kernel}
In this section, we briefly desbribe an efficient kernel named NSPDK \cite{nspdk} which allows to measure the similarity between labeled graphs. NSPDK is an instance of decompositional kernel \cite{convolution-kernel}.

Given a labeled graph $G \in \mathcal{G}$ and two rooted graphs $A_u, B_v$, we first define the relation $R_{r,d}(A_u, B_v, G)$ to be true {\em iff} $A_u \cong \mathcal{N}_r^u$ is (up to isomorphism $\cong$) a neighborhood subgraph with radius $r$ of $G$ and so is $B_v \cong  \mathcal{N}_r^v$, such that $v$ is a distance $d$ from $u$: $\mathcal{D}(u,v)= d$. We then define the inverse relation $R^{-1}$ that returns all pairs of neighborhoods of radius $r$ at distance $d$ in $G$, $R^{-1}_{r,d}(G) = \lbrace A_u, B_v | R_{r,d}(A_u,B_v,G)=true\rbrace$. The kernel $\kappa_{r,d}$ over $\mathcal{G} \times \mathcal{G}$ is the number of such fragments in common in two input graphs:
\begin{center}
$\kappa_{r,d}(G,G^{'}) = 
\!\!\!\!\!\!\!\!\!\!\!\! 
\sum\limits_{\substack{A_u, B_v \ \in \ R_{r,d}^{-1}(G) \\ 
{A'}_{u'}, {B'}_{v'} \ \in \ R_{r,d}^{-1}(G')
}} \!\!\!\!\!\!\!\!\!\!\!\!  { { \textbf{1}_{A_{u} \cong A'_{u'}}} \cdot {
\textbf{1}_{B_{v} \cong B'_{v'}}} }$, 
\end{center}
\noindent where $\textbf{1}_{A \cong B}$ is the \textit{exact matching function} that returns 1 if $A$ is isomorphic to $B$ and 0 otherwise. Finally, the NSPDK is defined as $K(G,G') = \sum\limits_{r}{\sum\limits_{d}{\kappa_{r,d}(G,G')}}$, where for efficiency reasons, the values of $r$ and $d$ are upper bounded to a given maximal $r^*$ and $d^*$, respectively.

Related to exact matching function, this function needs to solve the graph isomorphism problem. This problem is not known to be solvable in polynomial time nor to be NP-complete. In \cite{nspdk}, they propose an approximate method to figure out graph isomorphism problem. It first transforms graphs into strings. It then employ a hash function to map each unique string with an integer number. Finally, two graphs are isomorphic if they have the same corresponding integer numbers.

@@

\item \textit{Metabolic} \cite{metabolic}: a biological network which relates enzyme proteins and chemical compounds and it includes 668 nodes and 2782 links.

\item \textit{Nips} \cite{nips}: a network of co-authors at NIPS conference from first to twelfth edition. Nodes are authors and links encode co-author relation between authors. This network contains 2865 nodes and 4733 links.

@@

\item \textit{Conflict} \cite{conflict1}, \cite{conflict2}: a network describing the dispute between 130 countries. A link connecting two nodes (countries) if they dispute. We have 180 links in total in this network.

@@

\hline
         & \multicolumn{6}{c|}{\textbf{Datasets}}\\
 \hline
\textbf{Methods} & Protein & Metabolic & Nips & Condmat & Conflict & PowerGrid\\
\hline
AA & 56.4$\pm$0.5 & 52.4$\pm$0.5 & 51.2$\pm$0.2 & 56.7$\pm$1.4 & 50.7$\pm$0.8 & 58.9$\pm$0.3\\
PA & 75.0$\pm$0.3 & 52.4$\pm$0.5 & 54.3$\pm$0.5 & 71.6$\pm$2.6 & 54.6$\pm$2.4 & 44.2$\pm$01.0\\
SHP & 72.6$\pm$0.5 & 62.6$\pm$0.4 & 51.7$\pm$0.3 & 67.3$\pm$1.8 & 51.2$\pm$1.4 & 65.9$\pm$1.5\\
Katz & 72.7$\pm$0.5 & 60.8$\pm$0.7 & 51.7$\pm$0.3 & 67.3$\pm$1.7 & 51.2$\pm$1.4 & 65.5$\pm$1.6 \\
Sup-Top & 75.4$\pm$0.3 & 62.8$\pm$0.1 & 54.2$\pm$0.7 & 72.0$\pm$2.0 & 69.5$\pm$7.6 & 70.8$\pm$6.2\\
SVD & 63.5$\pm$0.3 & 53.8$\pm$1.7 & 51.2$\pm$3.1 & 62.9$\pm$5.1 & 54.1$\pm$9.4 & 69.1$\pm$2.6\\
Fact+Scores & 79.3$\pm$0.5 & 69.6$\pm$0.2 & 61.3$\pm$1.9 & 81.2$\pm$2.0 & 68.9$\pm$4.2 & 75.1$\pm$2.0 \\
JNSL & \textbf{80.1$\pm$0.8} & \textbf{72.5$\pm$0.7} & \textbf{62.1$\pm$0.8} & \textbf{88.6$\pm$2.3} & \textbf{72.0$\pm$0.9} & \textbf{75.6$\pm$0.7} \\
 \hline 
\end{tabular}
\label{result_table}
\end{table}
\section{Conclusion and Future Work}
In this paper, we have proposed an effective method for link prediction. Our method takes advantages from the way to represent links as joint neighborhood subgraphs and the employment of an convolution kernel that is able to efficiently exploit the graph structure. The results from the experiment show that our method is the state of the art for graph structured link prediction, especially when the side information are not available.
